EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
intro, bits and bobs

\newcommand{\EVOSUITE}{{\sc EvoSuite}\xspace}
\newcommand{\MUTEST}{{\sc $\mu$Test}\xspace}
\newcommand{\CS}{{\sc SF100}\xspace}

@@

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 5th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2017, four tools competed on a set of open source Java
classes. This paper describes the results of applying the \EVOSUITE
test generation tool~\cite{FrA11c} in this competition. Details about
the procedure of the competition, the technical framework, and the
benchmark classes can be found in~\cite{sbst17competition}.  In this
competition, \EVOSUITE achieved a 1457.3 overall score, which was the
highest among the competing and baseline tools.

@@

\begin{table}[!h]
\renewcommand{\arraystretch}{1.3}
\caption{Classification of the \EVOSUITE unit test generation
  tool.}\label{tool-description}
\resizebox{1.0\columnwidth}{!}{  
\begin{tabular}{|l|p{5cm}|}
  \hline
  \multicolumn{2}{|l|}{Prerequisites} \\
  \hline
  Static or dynamic &  Dynamic testing at the Java class level\\
  Software Type &  Java classes\\
  Lifecycle phase&  Unit testing for Java programs\\
  Environment&  All Java development environments \\
  Knowledge required & JUnit unit testing for Java\\
  Experience required &  Basic unit testing knowledge\\
 \hline
  \multicolumn{2}{|l|}{Input and Output of the tool} \\
  \hline
 Input & Bytecode of the target class and dependencies \\
\hline
Output&  JUnit 4 test cases\\

  \hline
  \multicolumn{2}{|l|}{Operation} \\
  \hline
  Interaction &  Through the command line, and plugins for IntelliJ, Maven and Eclipse\\
  User guidance &  manual verification of assertions for functional faults\\
  Source of information &  http://www.evosuite.org \\
  Maturity&  Mature research prototype, under development\\
  Technology behind the tool & Search-based testing / whole test suite generation\\
\hline
  \multicolumn{2}{|l|}{Obtaining the tool and information} \\
  \hline
License & Lesser GPL V.3\\
Cost & Open source\\
Support & None \\
\hline
\hline
  \multicolumn{2}{|l|}{Does there exist empirical evidence about} \\
  \hline
  Effectiveness and Scalability & See~\cite{GoA_TSE12,fraser2014large}. \\
%Completeness & \\
%Effectiveness & \\
%Efficiency & \\
%Defect types & \\
%Scalability & \\
%Comprehensibility & \\
%Learnability & \\
%Subjective satisfaction & \\
%Other & \\
\hline
\end{tabular}\vspace{-1em}
}
\end{table}

@@

%------------------------------------------------------------------------- 
\section{Benchmark results}

@@

\subsection{Overall results}

@@

\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
much lower than the number of flaky tests produced by the competing
and baseline tools (\FlakyTthree by T3, \FlakyJtexpert by JTExpert, and
\FlakyRandoop by Randoop). We attribute these results---also
consistent with previous years' results---to the way \EVOSUITE handles
execution environments during test generation (e.g., controlling the
static state of the class under test, mocking interactions with the
file system, system calls like \texttt{System.in} and
\texttt{System.currentTimeMillis}, etc.)~\cite{arcuri2014automated}.

>>>>

\newcommand{\EVOSUITE}{{\sc EvoSuite}\xspace}
\newcommand{\JTEXPERT}{{\sc jTExpert}\xspace}
\newcommand{\RANDOOP}{{\sc Randoop}\xspace}
\newcommand{\TT}{{\sc T3}\xspace}

\newcommand{\MUTEST}{{\sc $\mu$Test}\xspace}
\newcommand{\CS}{{\sc SF100}\xspace}

@@

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 5th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2017, two tools, \EVOSUITE and \JTEXPERT, competed on a
set of 69 open-source Java classes. Two other tools, \RANDOOP and \TT,
and existing open-source test suites were used as baseline. This paper
describes the results obtained by the \EVOSUITE test generation
tool~\cite{FrA11c} in this competition. Details about the procedure of
the competition, the technical framework, and the benchmark classes
can be found in~\cite{sbst17competition}.  In this competition,
\EVOSUITE achieved a 1457.3 overall score, which was the highest among
the competing and baseline tools.

@@

\begin{table}[!h]
\renewcommand{\arraystretch}{1.3}
\caption{Classification of the \EVOSUITE unit test generation
  tool}\label{tool-description}
\resizebox{1.0\columnwidth}{!}{  
\begin{tabular}{|l|p{5cm}|}
  \hline
  \multicolumn{2}{|l|}{Prerequisites} \\
  \hline
  Static or dynamic &  Dynamic testing at the Java class level\\
  Software Type &  Java classes\\
  Lifecycle phase&  Unit testing for Java programs\\
  Environment&  All Java development environments \\
  Knowledge required & JUnit unit testing for Java\\
  Experience required &  Basic unit testing knowledge\\
 \hline
  \multicolumn{2}{|l|}{Input and Output of the tool} \\
  \hline
 Input & Bytecode of the target class and dependencies \\
\hline
Output&  JUnit 4 test cases\\

  \hline
  \multicolumn{2}{|l|}{Operation} \\
  \hline
  Interaction &  Through the command line, and plugins for IntelliJ, Maven and Eclipse\\
  User guidance &  Manual verification of assertions for functional faults\\
  Source of information &  http://www.evosuite.org \\
  Maturity&  Mature research prototype, under development\\
  Technology behind the tool & Search-based testing / whole test suite generation\\
\hline
  \multicolumn{2}{|l|}{Obtaining the tool and information} \\
  \hline
License & Lesser GPL V.3\\
Cost & Open source\\
Support & None \\
\hline
\hline
  \multicolumn{2}{|l|}{Does there exist empirical evidence about} \\
  \hline
  Effectiveness and Scalability & See~\cite{GoA_TSE12,fraser2014large} \\
%Completeness & \\
%Effectiveness & \\
%Efficiency & \\
%Defect types & \\
%Scalability & \\
%Comprehensibility & \\
%Learnability & \\
%Subjective satisfaction & \\
%Other & \\
\hline
\end{tabular}\vspace{-1em}
}
\end{table}

@@

%------------------------------------------------------------------------- 
\section{Benchmark Results}

@@

\subsection{Overall Results}

@@

\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
much lower than the number of flaky tests produced by the competing
and baseline tools (\FlakyTthree by \TT, \FlakyJtexpert by \JTEXPERT,
and \FlakyRandoop by \RANDOOP). We attribute these results---also
consistent with previous years' results---to the way \EVOSUITE handles
execution environments during test generation (e.g., controlling the
static state of the class under test, mocking interactions with the
file system, system calls like \texttt{System.in} and
\texttt{System.currentTimeMillis}, etc.)~\cite{arcuri2014automated}.
